Results Text

### 2024-03-13 Fish Data Analysis/Paper_Figures.qmd
Edits for paper

my_comparisons <- list(c("No Ablation, Light", "No Ablation, Dark"),
                       c("No Ablation, Light", "Ablated, Dark"), 
                       c("Ablated, Light", "No Ablation, Dark"),
                       c("Ablated, Light", "Ablated, Dark"))

@@

my_comparisons <- list(c("No Ablation, Light", "Ablated, Dark"), c("Ablated, Light", "Ablated, Dark"))

nnd_flow <- ggplot(school_data %>% filter(Flow == "Flowing Water (2 BL/s)"),
       aes(x = interaction(Ablation,Darkness,sep=", "), y = NND,
           color = interaction(Ablation,Darkness,sep=", "),
           fill = interaction(Ablation,Darkness,sep=", ")))+
  stat_dots(side = "both", binwidth = unit(dot_binwidth, "npc")) +
  geom_point(aes(y = NND_Mean_Val), size = 5, color = "Black") +
  geom_errorbar(aes(ymin=NND_Mean_Val-NND_SD_Val, ymax=NND_Mean_Val+NND_SD_Val), width=.2, color = "Black")+
  guides(fill = guide_legend(title = "Condition")) +
  scale_fill_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color, dark_ab_color)) +
  scale_color_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color, dark_ab_color)) +
  #ggtitle("Effect of Available Senses on Nearest Neighbor Distance (NND) in Flow (2 BL/s)") +
  xlab("") +
  ylab("School NND (BL)") +
  theme_light()+ 
  theme(legend.position = "none") +
  #ylim(0,2.5)+
  stat_compare_means(comparisons = my_comparisons, label = "p.signif", hide.ns = TRUE) +
  theme(axis.text.x = element_text(size = text_size),
        axis.text.y = element_text(size = text_size),
        axis.title.y = element_text(size = text_size))+
  scale_x_discrete(labels=function(x){sub(",\\s", "\n", x)})

@@

polar_still <- ggplot(school_data %>% filter(Flow == "Still Water"),
       aes(x = interaction(Ablation,Darkness,sep=", "), y = School_Polar,
           color = interaction(Ablation,Darkness,sep=", "),
           fill = interaction(Ablation,Darkness,sep=", ")))+
  stat_dots(side = "both", binwidth = unit(dot_binwidth, "npc")) +
  geom_point(aes(y = Polar_Mean_Val), size = 5, color = "Black") +
  geom_errorbar(aes(ymin=Polar_Mean_Val-Polar_SD_Val, ymax=Polar_Mean_Val+Polar_SD_Val), width=.2, color = "Black")+
  guides(fill = guide_legend(title = "Condition")) +
  scale_fill_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color, dark_ab_color)) +
  scale_color_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color, dark_ab_color)) +
  #ggtitle("Effect of Available Senses on Polarization in Still Water") +
  xlab("") +
  ylab("Polarization") +
  theme_light()+ 
  theme(legend.position = "none") +
  ylim(0,1.15)+
  stat_compare_means(comparisons = my_comparisons, label = "p.signif", hide.ns = TRUE) +
  theme(axis.text.x = element_text(size = text_size),
        axis.text.y = element_text(size = text_size),
        axis.title.y = element_text(size = text_size))+
  scale_x_discrete(labels=function(x){sub(",\\s", "\n", x)})

polar_flow <- ggplot(school_data %>% filter(Flow == "Flowing Water (2 BL/s)"),
       aes(x = interaction(Ablation,Darkness,sep=", "), y = School_Polar,
           color = interaction(Ablation,Darkness,sep=", "),
           fill = interaction(Ablation,Darkness,sep=", ")))+
  stat_dots(side = "both", binwidth = unit(dot_binwidth, "npc")) +
  geom_point(aes(y = Polar_Mean_Val), size = 5, color = "Black") +
  geom_errorbar(aes(ymin=Polar_Mean_Val-Polar_SD_Val, ymax=Polar_Mean_Val+Polar_SD_Val), width=.2, color = "Black")+
  guides(fill = guide_legend(title = "Condition")) +
  scale_fill_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color, dark_ab_color)) +
  scale_color_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color, dark_ab_color)) +
  #ggtitle("Effect of Available Senses on Polarization in Flowing Water (2 BL/s)") +
  xlab("") +
  ylab("Polarization") +
  theme_light()+ 
  theme(legend.position = "none") +
  ylim(0,1.15)+
  stat_compare_means(comparisons = my_comparisons, label = "p.signif", hide.ns = TRUE) +
  theme(axis.text.x = element_text(size = text_size),
        axis.text.y = element_text(size = text_size),
        axis.title.y = element_text(size = text_size))+
  scale_x_discrete(labels=function(x){sub(",\\s", "\n", x)})

@@

polar_glm <- glm(School_Polar ~ Ablation*Darkness*Flow, data = school_data)
Anova(polar_glm)
emmeans(polar_glm, specs = pairwise ~ Ablation:Darkness | Flow)

polar_glm_still <- glm(School_Polar ~ Ablation*Darkness, data = school_data %>% filter(Flow == "Still Water"))
Anova(polar_glm_still, test.statistic="F")

polar_glm_flow <- glm(School_Polar ~ Ablation*Darkness, data = school_data %>% filter(Flow == "Flowing Water (2 BL/s)"))
Anova(polar_glm_flow, test.statistic="F")
```

@@

```{r}
my_comparisons <- list()

@@

my_comparisons <- list(c("No Ablation, Light", "Ablated, Light"))

@@

speed_glm <- glm(School_Speed ~ Ablation*Darkness*Flow, data = school_data)
Anova(speed_glm)
emmeans(speed_glm, specs = pairwise ~ Ablation:Darkness | Flow)

speed_glm_still <- glm(School_Speed ~ Ablation*Darkness, data = school_data %>% filter(Flow == "Still Water"))
Anova(speed_glm_still, test.statistic="F")

speed_glm_flow <- glm(School_Speed ~ Ablation*Darkness, data = school_data %>% filter(Flow == "Flowing Water (2 BL/s)"))
Anova(speed_glm_flow, test.statistic="F")
```

>>>>

my_comparisons <- list(c("No Ablation, Light", "No Ablation, Dark"),
                       c("Ablated, Light", "No Ablation, Dark"),
                       c("Ablated, Light", "Ablated, Dark"))

@@

my_comparisons <- list(c("No Ablation, Light", "Ablated, Light"),
                       #c("No Ablation, Light", "Ablated, Dark"),
                       c("Ablated, Light", "No Ablation, Dark"))

nnd_flow <- ggplot(school_data %>% filter(Flow == "Flowing Water (2 BL/s)"),
       aes(x = interaction(Ablation,Darkness,sep=", "), y = NND,
           color = interaction(Ablation,Darkness,sep=", "),
           fill = interaction(Ablation,Darkness,sep=", ")))+
  stat_dots(side = "both", binwidth = unit(dot_binwidth, "npc")) +
  geom_point(aes(y = NND_Mean_Val), size = 5, color = "Black") +
  geom_errorbar(aes(ymin=NND_Mean_Val-NND_SD_Val, ymax=NND_Mean_Val+NND_SD_Val), width=.2, color = "Black")+
  guides(fill = guide_legend(title = "Condition")) +
  scale_fill_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color, dark_ab_color)) +
  scale_color_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color, dark_ab_color)) +
  #ggtitle("Effect of Available Senses on Nearest Neighbor Distance (NND) in Flow (2 BL/s)") +
  xlab("") +
  ylab("School NND (BL)") +
  theme_light()+ 
  theme(legend.position = "none") +
  #ylim(0,5)+
  stat_compare_means(comparisons = my_comparisons, label = "p.signif", hide.ns = TRUE) +
  theme(axis.text.x = element_text(size = text_size),
        axis.text.y = element_text(size = text_size),
        axis.title.y = element_text(size = text_size))+
  scale_x_discrete(labels=function(x){sub(",\\s", "\n", x)})

@@

polar_still <- ggplot(school_data %>% filter(Flow == "Still Water"),
       aes(x = interaction(Ablation,Darkness,sep=", "), y = School_Polar,
           color = interaction(Ablation,Darkness,sep=", "),
           fill = interaction(Ablation,Darkness,sep=", ")))+
  stat_dots(side = "both", binwidth = unit(dot_binwidth, "npc")) +
  geom_point(aes(y = Polar_Mean_Val), size = 5, color = "Black") +
  geom_errorbar(aes(ymin=Polar_Mean_Val-Polar_SD_Val, ymax=Polar_Mean_Val+Polar_SD_Val), width=.2, color = "Black")+
  guides(fill = guide_legend(title = "Condition")) +
  scale_fill_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color, dark_ab_color)) +
  scale_color_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color, dark_ab_color)) +
  #ggtitle("Effect of Available Senses on Polarization in Still Water") +
  xlab("") +
  ylab("Polarization") +
  theme_light()+ 
  theme(legend.position = "none") +
  #ylim(0,1.15)+
  stat_compare_means(comparisons = my_comparisons, label = "p.signif", hide.ns = TRUE) +
  theme(axis.text.x = element_text(size = text_size),
        axis.text.y = element_text(size = text_size),
        axis.title.y = element_text(size = text_size))+
  scale_x_discrete(labels=function(x){sub(",\\s", "\n", x)})

my_comparisons <- list(c("No Ablation, Light","Ablated, Dark"),
                       c("Ablated, Light","Ablated, Dark"),
                       c("No Ablation, Dark","Ablated, Dark"))

polar_flow <- ggplot(school_data %>% filter(Flow == "Flowing Water (2 BL/s)"),
       aes(x = interaction(Ablation,Darkness,sep=", "), y = School_Polar,
           color = interaction(Ablation,Darkness,sep=", "),
           fill = interaction(Ablation,Darkness,sep=", ")))+
  stat_dots(side = "both", binwidth = unit(dot_binwidth, "npc")) +
  geom_point(aes(y = Polar_Mean_Val), size = 5, color = "Black") +
  geom_errorbar(aes(ymin=Polar_Mean_Val-Polar_SD_Val, ymax=Polar_Mean_Val+Polar_SD_Val), width=.2, color = "Black")+
  guides(fill = guide_legend(title = "Condition")) +
  scale_fill_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color, dark_ab_color)) +
  scale_color_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color, dark_ab_color)) +
  #ggtitle("Effect of Available Senses on Polarization in Flowing Water (2 BL/s)") +
  xlab("") +
  ylab("Polarization") +
  theme_light()+ 
  theme(legend.position = "none") +
  #ylim(0,2)+
  stat_compare_means(comparisons = my_comparisons, label = "p.signif", hide.ns = TRUE) +
  theme(axis.text.x = element_text(size = text_size),
        axis.text.y = element_text(size = text_size),
        axis.title.y = element_text(size = text_size))+
  scale_x_discrete(labels=function(x){sub(",\\s", "\n", x)})

@@

polar_glm <- glm(School_Polar ~ Ablation*Darkness*Flow, data = school_data)
Anova(polar_glm)
emmeans(polar_glm, specs = pairwise ~ Ablation:Darkness | Flow)
```

@@

```{r}
my_comparisons <- list(c("No Ablation, Light", "Ablated, Dark"),
                       c("No Ablation, Dark", "Ablated, Dark"))

@@

my_comparisons <- list(c("No Ablation, Light", "Ablated, Dark"))

@@

speed_glm <- glm(School_Speed ~ Ablation*Darkness*Flow, data = school_data)
Anova(speed_glm)
emmeans(speed_glm, specs = pairwise ~ Ablation:Darkness | Flow)
```

### 2024-03-13 Fish Data Analysis/Results_Text.qmd
Edits for paper

@@

@@

@@

@@

@@

groups_lmer_still <- lmer(Groups ~ Ablation*Darkness + (1|Date), data = school_data %>% filter(Flow == "Still Water"))
groups_s_aov_me <- Anova(groups_lmer_still)

groups_lmer_flow <- lmer(Groups ~ Ablation*Darkness + (1|Date), data = school_data %>% filter(Flow == "Flowing Water (2 BL/s)"))
groups_f_aov_me <- Anova(groups_lmer_flow)

@@

heading_PS_model_close <- lmer(0 + Fish1_Yaw_Heading_PS ~ sin(Angle) + sin(Angle):Ablation + sin(Angle):Darkness + sin(Angle):Ablation:Darkness + (1|Date), 
                   data = fish_data_nn_normal_close %>% filter(Flow == "Still Water")) 
aov_heading_PS_model_close <- Anova(heading_PS_model_close)

@@

heading_PS_model_far <- lmer(0 + Fish1_Yaw_Heading_PS ~ sin(Angle) + sin(Angle):Ablation + sin(Angle):Darkness + sin(Angle):Ablation:Darkness + (1|Date) , 
                   data = fish_data_nn_normal_far %>% filter(Flow == "Still Water")) 
aov_heading_PS_model_far <- Anova(heading_PS_model_far)

>>>>

plot(nnd_lmer_still)
qqnorm(resid(nnd_lmer_still))
qqline(resid(nnd_lmer_still))

@@

plot(nnd_lmer_flow)
qqnorm(resid(nnd_lmer_flow))
qqline(resid(nnd_lmer_flow))

@@

plot(polar_lmer_still)
qqnorm(resid(polar_lmer_still))
qqline(resid(polar_lmer_still))

@@

plot(polar_lmer_flow)
qqnorm(resid(polar_lmer_flow))
qqline(resid(polar_lmer_flow))

@@

plot(speed_lmer_still)
qqnorm(resid(speed_lmer_still))
qqline(resid(speed_lmer_still))

@@

plot(speed_lmer_flow)
qqnorm(resid(speed_lmer_flow))
qqline(resid(speed_lmer_flow))

groups_lmer_still <- glmer(Groups ~ Ablation*Darkness + (1|Date), data = school_data %>% filter(Flow == "Still Water"),
                           family = poisson)
groups_s_aov_me <- Anova(groups_lmer_still)

plot(groups_lmer_still)
qqnorm(resid(groups_lmer_still))
qqline(resid(groups_lmer_still))

groups_lmer_flow <- glmer(Groups ~ Ablation*Darkness + (1|Date), data = school_data %>% filter(Flow == "Flowing Water (2 BL/s)"),
                           family = poisson)
groups_f_aov_me <- Anova(groups_lmer_flow)

plot(groups_lmer_flow)
qqnorm(resid(groups_lmer_flow))
qqline(resid(groups_lmer_flow))

@@

heading_PS_model_close <- lmer(Fish1_Yaw_Heading_PS ~ sin(Angle) + sin(Angle):Ablation + sin(Angle):Darkness + sin(Angle):Ablation:Darkness + (1|Date), 
                   data = fish_data_nn_normal_close %>% filter(Flow == "Still Water")) 
aov_heading_PS_model_close <- Anova(heading_PS_model_close)

plot(heading_PS_model_close)
qqnorm(resid(heading_PS_model_close))
qqline(resid(heading_PS_model_close))

@@

heading_PS_model_far <- lmer(Fish1_Yaw_Heading_PS ~ sin(Angle) + sin(Angle):Ablation + sin(Angle):Darkness + sin(Angle):Ablation:Darkness + (1|Date) , 
                   data = fish_data_nn_normal_far %>% filter(Flow == "Still Water")) 
aov_heading_PS_model_far <- Anova(heading_PS_model_far)

plot(heading_PS_model_far)
qqnorm(resid(heading_PS_model_far))
qqline(resid(heading_PS_model_far))
